---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# mixtape

<!-- badges: start -->
<!-- badges: end -->

> Turns out there is already another version of this package, with better documentation of the data sets: https://github.com/johnson-shuffle/mixtape. I suggest using that instead.

<br/>

This package contains the data sets for ["Causal Inference: The Mixtape"](http://scunning.com/mixtape.html).

## Installation

You can install the latest version of mixtape with:

``` r
# install.packages("remotes")
remotes::install_github("mpaulacaldas/mixtape")
```

## Usage

To see a list of the data sets included in this package, type:

```{r example}
data(package = "mixtape")
```

After you have loaded the package, you can use a data set by calling it by its name:

```{r}
library(mixtape)

head(acemogluetal)
```

